SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
fix figure
review Incorporating System Models to Automated Verification Procedures

Figure~\ref{intelligent-product} shows some examples of embedded systems, which typically consist of a human-machine interface ({\it e.g.}, keyboard and LCD), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) \cite{Kopetz11}. Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.
%

\textcolor{red}{mudei o texto e coloquei a ref do Kopetz... na figura 1, falta ligar as frases ``multi-core processors'' e ``limited amount of energy'' com um ``with''}

\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{An embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}

@@

Indeed, research in software verification is now incorporating such considerations, during checking processes, and some schemes already use knowledge about the system to be verified and the underlying hardware. Recently, a verification tool for digital systems was proposed, which is called digital system verifier (DSVerifier)~\cite{dsv_spin2015} and is able to aid engineers to check overflow, limit cycle, output error, timing, stability, and minimum phase, considering finite word-length effects. Indeed, DSVerifier is a useful test tool, which takes into account realization forms ({\it e.g.}, direct forms, delta forms, and transposed forms) and other implementation restrictions to explore the design space. Ultimately, if the system requirements are not met with a given configuration, an analysis of the provided error report may suggest another setup.

>>>>

Figure~\ref{intelligent-product} shows some examples of embedded systems, which typically consist of a human-machine interface ({\it e.g.}, keyboard and LCD), a processing unit ({\it e.g.}, real-time computer system), and an instrumentation interface ({\it e.g.}, sensor, network, and actuator) \cite{Kopetz11}. Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{An embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}

@@

Indeed, research in software verification is now incorporating such considerations, during checking processes, and some schemes already use knowledge about the system to be verified and the underlying hardware. Recently, a verification tool for digital systems was proposed, which is called digital system verifier (DSVerifier)~\cite{dsv_spin2015} and is able to aid engineers to check overflow, limit cycle, output error, timing, stability, and minimum phase, considering finite word-length (FWL) effects. Additionally, DSVerifier checks closed-loop systems with uncertain models considering FWL effects, which are typically represented as hybrid systems, {\it i.e.}, the controller is digital but the controlled agent (plant) is a physical and continuous system. Here, the verification procedure has to consider the interaction between a continuous plant and a digital (and sampled) controller with FWL effects, which can be connected using different control system configurations. Indeed, DSVerifier is a useful test tool, which takes into account different realization forms ({\it e.g.}, direct forms, delta forms, and transposed forms) and other implementation restrictions to explore the design space. Ultimately, if the system requirements are not met with a given configuration, an analysis of the provided error report may suggest another setup.
